---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# WordsChars

<!-- badges: start -->
<!-- badges: end -->

The goal of WordsChars is to count the number of characters and words in a given string.
You can decide weather you want to count spaces as character or not. When given a string to count, you will
get a vector in return whose first element is the number of characters and second element is the number of words.

## Installation

WordsChars is not yet in CRAN. But, you can install the development version of WordsChars like so:



``` r
devtools::install_github("jburckhardt/WordsChars")

```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(WordsChars)
count_chr_words("Hello World", count_spaces = TRUE)
```

This package also allows you to **not** count spaces as characters!
```{r}
count_chr_words("Hello World", count_spaces = FALSE)
```

